---
title: "R Notebook"
output: html_notebook
---


```{r}

library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/cattle_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-05-01") & date_collected <= as.Date("2024-05-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Cattle EPG - May 2024",
     xlab= "Eggs per gram",
     col = "lightblue",
     border = "black")

```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/cattle_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-06-01") & date_collected <= as.Date("2024-06-30"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Cattle EPG - June 2024",
     xlab= "Eggs per gram",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/cattle_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-08-01") & date_collected <= as.Date("2024-08-30"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Cattle EPG - August 2024",
     xlab= "Eggs per gram",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/cattle_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-10-01") & date_collected <= as.Date("2024-10-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Cattle EPG - October 2024",
     xlab= "Eggs per gram",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/cattle_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-12-01") & date_collected <= as.Date("2024-12-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Cattle EPG - December 2024",
     xlab= "Eggs per gram",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/cattle_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-10-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Cattle EPG: May - October 2024",
     xlab= "Eggs per gram",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/cattle_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-12-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Cattle EPG: May - December 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/dairycow_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-6-30"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Dairy Cattle EPG: May - June 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/dairycow_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-10-01") & date_collected <= as.Date("2024-10-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Dairy Cattle EPG: October 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/beefcow_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-5-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Beef Cattle EPG: May 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/beefcow_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-6-01") & date_collected <= as.Date("2024-6-30"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Beef Cattle EPG: June 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/beefcow_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-8-01") & date_collected <= as.Date("2024-8-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Beef Cattle EPG: August 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/beefcow_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-8-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Beef Cattle EPG: May - August 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/sheep_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-10-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Sheep EPG: May - October 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/sheep_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-5-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Sheep EPG: May 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/sheep_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-6-01") & date_collected <= as.Date("2024-6-30"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Sheep EPG: June 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/sheep_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-8-01") & date_collected <= as.Date("2024-8-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Sheep EPG: July 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/sheep_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-8-01") & date_collected <= as.Date("2024-8-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Sheep EPG: August 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/sheep_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-10-01") & date_collected <= as.Date("2024-10-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Sheep EPG: October 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/goat_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-10-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Goat EPG: May - October 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/goat_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-10-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Goat EPG: May 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/goat_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-6-01") & date_collected <= as.Date("2024-6-30"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Goat EPG: June 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/goat_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-8-01") & date_collected <= as.Date("2024-8-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Goat EPG: August 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(dplyr)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/goat_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-10-01") & date_collected <= as.Date("2024-10-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))
hist(column_data,
     breaks=50,
     main="Goat EPG: October 2024",
     xlab= "EPG",
     col = "lightblue",
     border = "black")
```
```{r}
library(ggplot2)
library(readr)
library(lubridate)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/goat_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")
cattledata$month <- floor_date(cattledata$date_collected, "month")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-10-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))

ggplot(cattledata, aes(x = month)) +
  geom_histogram(stat = "count", fill = "skyblue", color = "black") +
  labs(title = "Goat Fecal Samples May - October 2024",
       x = "Month",
       y = "Number of Samples Collected") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
library(ggplot2)
library(readr)
library(lubridate)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/sheep_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")
cattledata$month <- floor_date(cattledata$date_collected, "month")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-10-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))

ggplot(cattledata, aes(x = month)) +
  geom_histogram(stat = "count", fill = "skyblue", color = "black") +
  labs(title = "Sheep Fecal Samples May - October 2024",
       x = "Month",
       y = "Number of Samples Collected") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
library(ggplot2)
library(readr)
library(lubridate)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/cattle_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")
cattledata$month <- floor_date(cattledata$date_collected, "month")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-12-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))

ggplot(cattledata, aes(x = month)) +
  geom_histogram(stat = "count", fill = "skyblue", color = "black") +
  labs(title = "Cattle Fecal Samples May - December 2024",
       x = "Month",
       y = "Number of Samples Collected") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
library(ggplot2)
library(readr)
library(lubridate)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/deer_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")
cattledata$month <- floor_date(cattledata$date_collected, "month")

subset_cattledata <- cattledata %>% filter(date_collected >= as.Date("2024-5-01") & date_collected <= as.Date("2024-12-31"))
column_data <- as.numeric(as.character(subset_cattledata$epg))

ggplot(cattledata, aes(x = month)) +
  geom_histogram(stat = "count", fill = "skyblue", color = "black") +
  labs(title = "Cattle Fecal Samples May - December 2024",
       x = "Month",
       y = "Number of Samples Collected") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
library(ggplot2)
library(readr)
library(lubridate)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/deer_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")
cattledata$month <- floor_date(cattledata$date_collected, "month")

monthly_avg <- cattledata %>%
  group_by(month) %>%
  summarise(avg_value = mean(epg, na.rm = TRUE))

ggplot(monthly_avg, aes(x = month, y = avg_value)) +
  geom_point(color = "blue", size = 4) +  # Dot plot
  labs(title = "White-tailed deer average EPG per month", x = "Month", y = "Average EPG") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
library(ggplot2)
library(readr)
library(lubridate)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/goat_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")
cattledata$month <- floor_date(cattledata$date_collected, "month")

monthly_avg <- cattledata %>%
  group_by(month) %>%
  summarise(avg_value = mean(epg, na.rm = TRUE))

ggplot(monthly_avg, aes(x = month, y = avg_value)) +
  geom_point(color = "blue", size = 4) +  # Dot plot
  labs(title = "Goat average EPG per month", x = "Month", y = "Average EPG") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
library(ggplot2)
library(readr)
library(lubridate)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/sheep_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")
cattledata$month <- floor_date(cattledata$date_collected, "month")

monthly_avg <- cattledata %>%
  group_by(month) %>%
  summarise(avg_value = mean(epg, na.rm = TRUE))

ggplot(monthly_avg, aes(x = month, y = avg_value)) +
  geom_point(color = "blue", size = 4) +  # Dot plot
  labs(title = "Sheep average EPG per month", x = "Month", y = "Average EPG") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
library(ggplot2)
library(readr)
library(lubridate)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/cattle_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")
cattledata$month <- floor_date(cattledata$date_collected, "month")

monthly_avg <- cattledata %>%
  group_by(month) %>%
  summarise(avg_value = mean(epg, na.rm = TRUE))

ggplot(monthly_avg, aes(x = month, y = avg_value)) +
  geom_point(color = "blue", size = 4) +  # Dot plot
  labs(title = "Cattle average EPG per month", x = "Month", y = "Average EPG") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
library(ggplot2)
library(readr)
library(lubridate)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/dairycow_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")
cattledata$month <- floor_date(cattledata$date_collected, "month")

monthly_avg <- cattledata %>%
  group_by(month) %>%
  summarise(avg_value = mean(epg, na.rm = TRUE))

ggplot(monthly_avg, aes(x = month, y = avg_value)) +
  geom_point(color = "blue", size = 4) +  # Dot plot
  labs(title = "Dairy cattle average EPG per month", x = "Month", y = "Average EPG") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
library(ggplot2)
library(readr)
library(lubridate)

cattledata <- read.csv("https://raw.githubusercontent.com/kaylaayana/Helminth-Data/refs/heads/main/beefcow_masterfile.csv", header = TRUE)

cattledata$date_collected <- as.Date(cattledata$date_collected,format = "%m/%d/%y")
cattledata$month <- floor_date(cattledata$date_collected, "month")

monthly_avg <- cattledata %>%
  group_by(month) %>%
  summarise(avg_value = mean(epg, na.rm = TRUE))

ggplot(monthly_avg, aes(x = month, y = avg_value)) +
  geom_point(color = "blue", size = 4) +  # Dot plot
  labs(title = "Beef cattle average EPG per month", x = "Month", y = "Average EPG") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

